On Secure Delegation of SampBQP with a Classical Client

### 2019-11-21 longoutput.tex
Work on new definitions

@@

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{Amplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

>>>>

First, for ease of notation, we write

We define and construct an instance of Local Hamiltonian that encodes the history of the computation.

\begin{definition}
	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
	\begin{itemize}
		\item can be written as...
		\item 0 eigenvalue ground state
		\item at least whatever eigenvalue in all other dimensions
		\item has ground state of a particular form we like
	\end{itemize}
\end{definition}

TODO Theorem statement for XZ LH and whatnot

@@

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{Amplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

### 2019-11-21 preliminaries.tex
Work on new definitions

\begin{definition}
	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

>>>>

\begin{definition}
	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	TODO Fix/redefine this to allow $\bbV$ a single qubit and ability to ONLY measure in X/Z
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

TODO Specialize above definition? Either ways make another one for purely classical $\bbV$.
